Complementary Filters Shaping Using $\mathcal{H}_\infty$ Synthesis

### 2019-10-30 poster/architecture.tex
Poster Finished

\begin{minipage}[t]{0.69\linewidth}
  The \textbf{complementary property} of \(H_1(s)\) and \(H_2(s)\) implies that their transfer function sum is equal to one at all frequencies:
\end{minipage}\hfill
\begin{minipage}[t]{0.29\linewidth}
  \vspace{-2em}
  \begin{equation*}
    \tcmbox{H_1(s) + H_2(s) = 1}
  \end{equation*}
\end{minipage}

>>>>

\begin{minipage}[t]{0.69\linewidth}
  The \textbf{complementary property} of \(H_1(s)\) and \(H_2(s)\) implies that their transfer function sum is equal to one at all frequencies.
\end{minipage}\hfill
\begin{minipage}[t]{0.29\linewidth}
  \vspace{-2em}
  \begin{equation*}
    \tcmbox{H_1(s) + H_2(s) = 1}
  \end{equation*}
\end{minipage}

### 2019-10-30 poster/requirements.tex
Add acknoledgments separate from reference. Work on Introduction
Poster Finished

  First suppose \textbf{perfectly known sensor dynamics} such that is can be
  inverted:
  \[ G_1(s) = G_2(s) = 1 \]

@@

  The PSD of the super sensor noise depends on the \textbf{norm} of the
  complementary filters:
  \[ \tcmbox{\Phi_{\delta x} = \left|H_1\right|^2 \Phi_{n_1} +
      \left|H_2\right|^2 \Phi_{n_2}} \]
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
  \begin{tikzfigure}[Fusion of sensors with dynamics uncertainty]
    \centering
    \label{fig:sensor_fusion_dynamic_uncertainty}
    \includegraphics[height=6cm]{figs/sensor_fusion_dynamic_uncertainty.pdf}
  \end{tikzfigure}

@@

  The obtained dynamic uncertainty depends on the \textbf{norm} of the filters (Fig.~\ref{fig:uncertainty_set_super_sensor}).

  \begin{tikzfigure}[Uncertainty set of the super sensor dynamics]
    \label{fig:uncertainty_set_super_sensor}
    \centering
    \includegraphics[width=0.8\linewidth]{figs/uncertainty_set_super_sensor.pdf}
  \end{tikzfigure}
\end{minipage}
\vspace{1em}
\sepline
\vspace{1em}

>>>>

  First suppose \textbf{perfectly known sensor dynamics} such that it can be
  inverted:
  \[ G_1(s) = G_2(s) = 1 \]

@@

  The PSD of the super sensor \textbf{noise} depends on the \textbf{norm} of the
  complementary filters:
  \[ \tcmbox{\Phi_{\delta x} = \left|H_1\right|^2 \Phi_{n_1} +
      \left|H_2\right|^2 \Phi_{n_2}} \]
\end{minipage}\hfill
\begin{minipage}[t]{0.47\linewidth}
  \begin{tikzfigure}[Fusion of sensors with dynamics uncertainty]
    \centering
    \label{fig:sensor_fusion_dynamic_uncertainty}
    \includegraphics[height=6cm]{figs/sensor_fusion_dynamic_uncertainty.pdf}
  \end{tikzfigure}

@@

  The obtained \textbf{dynamic uncertainty} depends on the \textbf{norm} of the filters (Fig.~\ref{fig:uncertainty_set_super_sensor}).

  \begin{tikzfigure}[Uncertainty set of the super sensor dynamics]
    \label{fig:uncertainty_set_super_sensor}
    \centering
    \includegraphics[width=0.8\linewidth]{figs/uncertainty_set_super_sensor.pdf}
  \end{tikzfigure}
\end{minipage}

\bigskip
\sepline
\bigskip
